Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-08-22 Multiresolution_framework/ltx/manuscript.tex
edits to 5.2

Two different experiments were designed to test the framework. In the first one, 200 realizations of 1 second of data were used, where the field disturbance, $e_t$, and the observation noise, $\boldsymbol\epsilon_t$, were regenerated each run. This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization. In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting up to a certain level of approximation, i.e. $j=0$ to $j=4$. \parham{We show it is possible to determine the level of approximation to accurately estimate the underlying field prior to the EM based algorithm.} All parameters for the model are given in Table~\ref{tab:Parameters}.

>>>>

Two different experiments were designed to test the framework. In the first one, 200 realizations of 1 second of data were used, where the field disturbance, $e_t$, and the observation noise, $\boldsymbol\epsilon_t$, were regenerated each run. This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization. In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting up to a certain level of approximation, i.e. $j=0$ to $j=4$. \parham{We show it is possible to determine the level of approximation to accurately estimate the underlying field prior to the EM-based algorithm.} All parameters for the model are given in Table~\ref{tab:Parameters}.
